Ecological Traitdata Standard

### 2017-06-21 docs/traitdatastandard.Rmd

---
title: "Ecological Traitdata Standard"
author: "Florian D. Schneider, Nadja Simons, Caterina Penone, Andreas Ostrowski"
date: "12 Mai 2017"
output: html_document
---

**This is the documentation of the Ecological Traitdata Standard (ETS), version 0.2**

This defined vocabulary aims at providing all essential columns for raw data of functional trait measurements for ecological research.

@@

The template is ordered into five different sections for column names, as well as a vocabulary for metadata information of particular importance for trait data.

1. Trait measurement data
2. Resolution of data / information on specimen
3. Data source / information on measurement
4. Measurement 
5. Location

@@

```{r, results = 'asis', echo = FALSE}
library(data.table)
library(knitr)
library(pander)
glossary <- read.csv("template_glossary.csv")

@@

 for(i in columnNames[sections == j]) {
     dd <- as.data.frame(t(glossary[[j]][[as.character(i)]]))
     colnames(dd) <- i
     print(kable(dd, format = "markdown"))
 }

@@

 for(i in columnNames[sections == j]) {
     dd <- as.data.frame(t(glossary[[j]][[i]]))
     colnames(dd) <- i
     print(kable(dd, format = "markdown"))
 }

>>>>

---
title: "Ecological Traitdata Standard"
author: "Florian D. Schneider, Nadja Simons, Caterina Penone, Andreas Ostrowski"
date: "12 Mai 2017"
output: 
  html_document: 
    keep_md: yes
    toc: yes
---

**This is the documentation of the Ecological Traitdata Standard (ETS), version 0.2** 
This defined vocabulary aims at providing all essential columns for raw data of functional trait measurements for ecological research.

@@

The template is ordered into six different sections, as well as a vocabulary for metadata information of particular importance for trait data.

1. Trait measurement data
2. Information about the Measurement or Fact
3. Resolution of data / information on specimen
4. Columns referring to sampling event or origin of record
5. Columns for aggregate measures 
6. Location information

@@

```{r, results = 'asis', echo = FALSE}
library(data.table)
library(knitr)
glossary <- read.csv("../template_glossary.csv")

@@

 for(i in columnNames[sections == j]) {
     dd <- as.data.frame(t(glossary[[j]][[as.character(i)]][,-1, with=FALSE]))
     colnames(dd) <- i
     cat("## `", i, "`  ", sep = "")
     print(kable(dd, format = "markdown"))
 }

@@

 for(i in columnNames[sections == j]) {
    dd <- as.data.frame(t(glossary[[j]][[as.character(i)]][,-1, with=FALSE]))
     colnames(dd) <- i
     cat("## `", i, "`  ", sep = "")
 print(kable(dd, format = "markdown"))
 }
